Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-02-26 publication_materials/ms_rbc.tex

A novel iterative time-marching method is derived by introducing time-dependence in the background temperature profile of the classical Rayleigh-B\'enard Boussinesq linear stability analysis. Eigenfunction amplitudes are obtained by requiring marginal-stability. Symmetric thermally-equilibrated states are then obtained and their intrinsic properties are analyzed. Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations: marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$. 2-dimensional simulations run with thermally-equilibrated initial conditions turn out to be kinetically exaggerated, consequently requiring increased computational expense when compared to the conventional diffusive initial condition.

@@

The introduction leads the reader from a general subject area to a particular topic of inquiry. It establishes the scope, context, and significance of the research being conducted by summarizing current understanding and background information about the topic, stating the purpose of the work in the form of the research problem supported by a hypothesis or a set of questions, explaining briefly the methodological approach used to examine the research problem, highlighting the potential outcomes your study can reveal, and outlining the remaining structure and organization of the paper.

>>>>

boiii A novel iterative time-marching method is derived by introducing time-dependence in the background temperature profile of the classical Rayleigh-B\'enard Boussinesq linear stability analysis. Eigenfunction amplitudes are obtained by requiring marginal-stability. Symmetric thermally-equilibrated states are then obtained and their intrinsic properties are analyzed. Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations: marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$. 2-dimensional simulations run with thermally-equilibrated initial conditions turn out to be kinetically exaggerated, consequently requiring increased computational expense when compared to the conventional diffusive initial condition.

@@

boii The introduction leads the reader from a general subject area to a particular topic of inquiry. It establishes the scope, context, and significance of the research being conducted by summarizing current understanding and background information about the topic, stating the purpose of the work in the form of the research problem supported by a hypothesis or a set of questions, explaining briefly the methodological approach used to examine the research problem, highlighting the potential outcomes your study can reveal, and outlining the remaining structure and organization of the paper.
